New approaches for boosting to uniformity

### 2014-10-12 assets/paperdraft/parts/metrics.tex
update plots

%Let's start from reformulation of what is uniform predictions in signal. First we split all signal events into some bins in uniform variables. There is some empirical distribution $F_\bin$ of predictions in each bin. 
\begin{figure}[h]
		\centering
		\begin{subfigure}[b]{0.8\textwidth}
			\includegraphics[width=\textwidth]{graphs/bins_uniform_distribution.pdf}
			\caption{Predictions are uniform in mass, the distribution of predictions in the bin (yellow) is close to the global (blue).
			Yellow rectangle shows the events in the bin over mass.}
		\end{subfigure}
		\begin{subfigure}[b]{0.8\textwidth}
			\includegraphics[width=\textwidth]{graphs/bins_nonuniform_distribution.pdf}
			\caption{Distribution with peak in the middle, the distribution in the bin is quite different from global.}
		\end{subfigure}
		\caption{Demonstration of distribution similarity approach. \label{fig:dsavisualization}}
\end{figure}
Instead of measuring uniformity in terms of binned efficiencies, it is possible to consider the distribution of
the binned classifier predictions, $F_\bin$, directly.
Ideal uniformity means that all the distributions $F_\bin$ are equal and hence equal to the global distribution $F(x)$. 
This is demonstrated on figure \ref{fig:dsavisualization}.
To 'measure' non-flatness we can use some distribution distance, like Kolmogorov-Smirnov:
\[
	 \sum_{\bin} \binweight \max_x \abs{F_{\bin}(x) - F(x)},
\]
but Cram\'er--von Mises similarity is more informative (usually $p=2$ is used):
\[
	 \sum_{\bin} \binweight \int \abs{F_{\bin}(x) - F(x)}^p dF(x),
\]
in particular because Kolmogorov-Smirnov measures are too sensitive to local non-uniformities.
The advantage of this method is that we don't need to select some global efficiencies like in the previous metrics.
%\subsection{Connection Between SDE and Distribution Similarity Approach}
%Moreover, SDE and DSA based on Cram\'er--von Mises similarity can be shown to be connected.
%Let's consider the SDE with global efficiencies $= [1/N, 2/N, \dots, N/N]$. In the limit $N \to \infty$
%\[
%	\lim_{N \to \infty} \SDE^2 = 
%	\lim_{N \to \infty} \frac{1}{N} \sum_{\globaleff}\SDE^2(\globaleff) = 
%	\int_0^1 \SDE^2(\globaleff) d\, \globaleff = 
%	\int_0^1 \sum_{\bin} \binweight \abs{\bineff - \globaleff}^2 d\, \globaleff
%\]
%
%From the other side, we can write the expression for similarity-based measure (for $p=2$) 
%\[
%	\sum_{\bin} \binweight \int \abs{F_\text{bin}(x) - F(x)}^2 dF(x) =
%	\int \sum_{\bin} \binweight \abs{F_\text{bin}(x) - F(x)}^2 dF(x) 
%\] The hard thing now is to believe this is literally the same and these two expressions are equal.
%

@@

\begin{figure}[h]
\centering
	\includegraphics[width=0.5\textwidth]{graphs/TheilVsMSE.png}
	\caption{Comparison of SDE and Theil uniformity measures for different values of the constant $\alpha$ for the peak and pit distributions.
The Theil can clearly distinguish between these two while the SDE measure cannot.}
\end{figure}

@@

\subsubsection*{$D \to hhh$}
When our classifiers where applied to data set $D \to hhh$ we got uniformity measures for the SDE and Theil
metrics shown in Fig.~\ref{fig:d2hhhsdetheil}.
\begin{figure}[h]
\centering
		% TODO use metrics on signal for signal, use metrics on bck for bck.
		\begin{subfigure}[b]{0.95\textwidth}
			\includegraphics[width=\textwidth]{graphs/D23hSignalEffs.png}
			\caption{Metrics for $D \to hhh$ signal.}
		\end{subfigure}
		\begin{subfigure}[b]{0.95\textwidth}
			\includegraphics[width=\textwidth]{graphs/D23hBgEffs.png}
			\caption{Metrics for $D \to hhh$ background.}
		\end{subfigure}
		\caption{Uniformity metrics for the $D \to hhh$ data set. The (top) signal and (bottom) background uniformities are plotted as a function of the training stage of a given classifier, listed in the legends on the leftmost plots. \label{fig:d2hhhsdetheil}}
\end{figure}

Both metrics shown similar results, and that there is no significant difference on real data sets (as well as CvM).

>>>>

%Let's start from reformulation of what is uniform predictions in signal. First we split all signal events into some bins in uniform variables. There is some empirical distribution $F_\bin$ of predictions in each bin. 
\begin{figure}[h]
		\centering
		\begin{subfigure}[b]{0.48\textwidth}
			\includegraphics[width=\textwidth]{graphs/bins_uniform_distribution.pdf}
		\end{subfigure}
		\begin{subfigure}[b]{0.48\textwidth}
			\includegraphics[width=\textwidth]{graphs/bins_nonuniform_distribution.pdf}
		\end{subfigure}
		\caption{Demonstration of the distribution similarity approach. (left) Predictions are uniform in mass, the distribution of predictions in the bin (yellow) is close to the global (blue). (right) Distribution with peak in the middle, the distribution in the bin is quite different from the global distribution. In both cases the yellow rectangle shows the events in the bin over mass.\label{fig:dsavisualization}}
\end{figure}
Instead of measuring uniformity in terms of binned efficiencies, it is possible to consider the distribution of
the binned classifier predictions, $F_\bin$, directly.
Ideal uniformity means that all the distributions $F_\bin$ are equal and hence equal to the global distribution $F(x)$. 
This is demonstrated on figure \ref{fig:dsavisualization}.
To 'measure' non-flatness we can use some distribution distance, like Kolmogorov-Smirnov:
\[
	 \sum_{\bin} \binweight \max_x \abs{F_{\bin}(x) - F(x)},
\]
but Cram\'er--von Mises similarity is more informative (usually $p=2$ is used):
\[
	 \sum_{\bin} \binweight \int \abs{F_{\bin}(x) - F(x)}^p dF(x),
\]
in particular because Kolmogorov-Smirnov measures are too sensitive to local non-uniformities.
The advantage of this method is that we don't need to select some global efficiencies like in the previous metrics.
%\subsection{Connection Between SDE and Distribution Similarity Approach}
%Moreover, SDE and DSA based on Cram\'er--von Mises similarity can be shown to be connected.
%Let's consider the SDE with global efficiencies $= [1/N, 2/N, \dots, N/N]$. In the limit $N \to \infty$
%\[
%	\lim_{N \to \infty} \SDE^2 = 
%	\lim_{N \to \infty} \frac{1}{N} \sum_{\globaleff}\SDE^2(\globaleff) = 
%	\int_0^1 \SDE^2(\globaleff) d\, \globaleff = 
%	\int_0^1 \sum_{\bin} \binweight \abs{\bineff - \globaleff}^2 d\, \globaleff
%\]
%
%From the other side, we can write the expression for similarity-based measure (for $p=2$) 
%\[
%	\sum_{\bin} \binweight \int \abs{F_\text{bin}(x) - F(x)}^2 dF(x) =
%	\int \sum_{\bin} \binweight \abs{F_\text{bin}(x) - F(x)}^2 dF(x) 
%\] The hard thing now is to believe this is literally the same and these two expressions are equal.
%

@@

\begin{figure}[h]
\centering
	\includegraphics[width=0.9\textwidth]{graphs/TheilVsMSE.png}
	\caption{Comparison of SDE and Theil uniformity measures for different values of the constant $\alpha$ for the peak and pit distributions.
The Theil can clearly distinguish between these two while the SDE measure cannot.}
\end{figure}

@@

\subsubsection*{$D \to hhh$}
When our classifiers where applied to data set $D \to hhh$ we got uniformity measures for the SDE and Theil
metrics shown in Fig.~\ref{fig:d2hhhsdetheil}.
Both metrics show similar results, so there is no significant difference between them, nor the CvM metric, on this dataset.

\begin{figure}[h]
\centering
		% TODO use metrics on signal for signal, use metrics on bck for bck.
		\begin{subfigure}[b]{0.48\textwidth}
			\includegraphics[width=\textwidth]{graphs/D23hSignalEffs.png}
			\caption{Metrics for $D \to hhh$ signal.}
		\end{subfigure}
		\begin{subfigure}[b]{0.48\textwidth}
			\includegraphics[width=\textwidth]{graphs/D23hBgEffs.png}
			\caption{Metrics for $D \to hhh$ background.}
		\end{subfigure}
		\caption{Uniformity metrics for the $D \to hhh$ data set. The (top) signal and (bottom) background uniformities are plotted as a function of the training stage of a given classifier, listed in the legends on the leftmost plots. \label{fig:d2hhhsdetheil}}
\end{figure}
